On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-06-28 Manuscript/manuscript.tex
small changes

  \end{center}
\end{table}
The dataset of the four United States athletes 
is too small to perform any meaningful statistical analysis, but
the data was expanded to include reaction times for athletes who competed at 
national competitions (many of which were held from May-July of 2022). Once the 
data was collected, each athlete was designated as a cluster and the stage of
competition (national or international) was specified for each competition 
within the cluster (athlete).

@@

\subsection{2019 World Track and Field Championships}
The 2019 World Track and Field Championship data is included in the larger dataset
described in section~\ref{sec:databeyond}, but we can also use it similarly to
how we used national level in section~\ref{sec:datanational}.  We can compare
the times of athletes who participated in the 2019 and 2022 World Track and Field
Championships to see if there were lower times in 2022.  While it is theoretically
possible that athletes got faster between 2019 and 2022, it is important to
remember that these are some of the fastest sprinters on the planet, and thus
improving on elite times is not easy.  Nonetheless, this is a worthy inclusion
to the data because Seiko was the timing company responsible for both events,
the World Championships have the biggest stakes, and because

First we can compare the reaction times of 
athletes who
competed at the World Track and Field Championships in both 2019 and 2022, and 
then we can compare how athletes performed at the 2022 championships relative 
to their national/qualifiers meet. In order to reduce any chances
of athletes improving reaction time, we can also look at data from qualifying 
meets. Almost every athlete had to qualify by proving they are elite at the 
national level, usually by coming in at least fourth. Thus, data was compiled on 
athletes who competed at the 2022 World Track and Field Championships on what 
these athletes also ran at their country's national championship. If there was 
any argument that athletes
have improved their reaction time from 2019 to 2022, it should now be considered
nearly null, as the national competitions took place between June and July 2022 
and the World Championships were in August. The equipment used to measure 
reaction time cannot be guaranteed to be the same from national to international
competition, but the time span between meets has been reduced considerably.

>>>>

\end{center}
\end{table}

The dataset of the four United States athletes 
is too small to perform any meaningful statistical analysis, but
the data was expanded to include reaction times for athletes who competed at 
national competitions (many of which were held from May-July of 2022). Once the 
data was collected, each athlete was designated as a cluster and the stage of
competition (national or international) was specified for each competition 
within the cluster (athlete).

@@

\subsection{2019 World Track and Field Championships}
The 2019 World Track and Field Championship data is included in the larger dataset
described in section~\ref{sec:databeyond}, but we can also use it similarly to
how we used national level in section~\ref{sec:datanational}.  We can compare
the times of athletes who participated in the 2019 and 2022 World Track and Field
Championships to see if there were lower times in 2022.  While it is theoretically
possible that athletes got faster between 2019 and 2022, it is important to
remember that these are some of the fastest sprinters on the planet, and thus
improving on elite times is not easy.  Nonetheless, this is a worthy inclusion
to the data because Seiko was the timing company responsible for both events and
because the level of competition is the extremely elite in both cases.
